True versus apparent shapes of astrophysical bow shocks

### 2017-02-08 papers/Paper1/sec-thin-shell.tex
Add a figure to illustrate the CRW two-wind interaction problem
Add new figure to show anisotropic wind patterns

@@

In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
with the following density distribution:

\begin{align}
  n(\theta) = n_0\cos^k\theta
\end{align}  
The index $k$ gives the anisotropy degree. We are interested in winds where $k \geq 0$ for further applications. By the other side, we keep the strongest
wind as isotropic.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-crw-variables}
  \caption[]{Schematic diagram of two-wind interaction problem,
    following \citet{Canto:1996}.}
  \label{fig:crw-schema}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/anisotropic-arrows}
  \caption[]{Schematic diagram of wind flow patterns in isotropic and
    non-isotropic cases.  Arrows represent the wind momentum loss rate
    per solid angle.}
  \label{fig:crw-schema}
\end{figure}
In this work the weakest wind is modeled as an anisotropic hemispherical radial wind
with the following density distribution:
\begin{align}
  n(\theta) = n_0\cos^k\theta
\end{align}  
The index $k$ gives the anisotropy degree. We are interested in winds where $k \geq 0$ for further applications. By the other side, we keep the strongest
wind as isotropic.
